An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-01-12 poly-embed-arxiv-update/poly-embed-arxiv-update-clean.tex
Adding file for updated arxiv

\usepackage{float}
\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{lmodern}
\usepackage{hyperref}       % hyperlinks  %[implicit=false, bookmarks=false]
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[normalem]{ulem}
\usepackage{thm-restate}
\newcommand{\restatehack}[1]{}   % for auc-tex; don't ask
\usepackage{array}
\newcolumntype{R}{>{$}r<{$}} % math-mode version of "l" column type
\newcolumntype{C}{>{$}c<{$}} % math-mode version of "c" column type
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
%\usepackage[thmmarks, thref, amsthm]{ntheorem}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} % need xargs for below
%\usepackage{accents}
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1%
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}%TURN OFF FOR NOW \mytodo{gray}{#1}}
\ifnum\Comments=1               % fix margins for todonotes
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}%{\reals_{++}}
\newcommand{\dom}{\mathrm{dom}}

@@

% alphabetical order, by convention
\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}%\mathrm{int}(#1)}
\newcommand{\relint}{\mathrm{relint}}
%\newcommand{\inter}[1]{\mathring{#1}}%\mathrm{int}(#1)}
\newcommand{\inter}{\mathrm{inter}}
%\newcommand{\expectedv}[3]{\overline{#1}(#2,#3)}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} %xspace for use in text
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\hyp}{\mathrm{hypo}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
%\title{Consistent Polyhedral Surrogates via Embeddings}
%\title{Convex Surrogates via Polyhedral Losses}
\author{%
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}
 \and
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}
 \and
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}
}
\date{%                          % nice hack
  % \vspace*{-5pt}
  University of Colorado Boulder
  \\[15pt]
  \today
}
\begin{document}

@@

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
\raft{For journal submission: mention the applications (or just that we discuss them) briefly in prev sentence.}
We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
% The framework can generally be applied to finite prediction tasks, and is demonstrated on examples including high-confidence classification, structured prediction, ordered partitions, and top-$k$ prediction.
\end{abstract}

%\begin{keywords}%
%  property elicitation, proper scoring rules, surrogate loss functions, embeddings
%\end{keywords}

@@

%\raf{MOVED FROM SEC 2; maybe incorporate?}
%Often, for computational or other reasons, one is interested in a property $\gamma$ such as the mode, but wishes to elicit it by minimizing some other ``surrogate'' loss $L$ over some other space such as $\reals^d$, then mapping the result back to $\R$ using a link function.
%We now formalize this procedure.
%
%\jessie{ TODO Items 01 Mar 2021
%	\begin{itemize}
%		\item \sout{Reorg sections: \S 3 (Embeddings, matching risks, etc.), \S 5 (Calibrated link), Examples, \S 4 (Polyhedral losses: I.E. implies consistency) OR Main results (w/o proof), Examples, \S 3, \S 5, \S 4}
%		\item \sout{Flesh out and expand on Ordered Partition Example}
%		\item add paragraph of discussion on the requirements of polyhedral losses
%		\item Check proof and statement of Theorem~\ref{thm:poly-ie-implies-consistent} - Jessie, 17 Mar 21: took a look to brush up; Theorem~\ref{lem:ie-iff-embeds-refinement} can use a look too.
%		\item Try to make section~\ref{sec:poly-loss-embed} self-contained, moving up results from appendix 
%		\begin{itemize}
%		\item \sout{for now, move everything up except PDs}
%		\item see if you can isolate what exactly we need from PDs and state it as a new lemma (which is just about Bayes risks) \raf{*}
%		\item rethink proofs of Prop 1 and 2, see if we resolve the redundancy  \raf{*}
%		\end{itemize}
%		\item Make Cor 1 a Theorem: "For L polyhedral, ell discrete, L ind elic prop[ell] <==> L consistent wrt ell"
%\end{itemize}
%TODO Items summer 2020
%	\begin{itemize}
%		\item Formalize reverse implication proof of Proposition 1 with projections into the affine hull and back
%		\item Mention how our focus on polyhedral risks and general links extends DKR Section 3.1 (probably after Prop 1)
%		\item Replace Proposition 2 with Lemma 7?
%		\item Theorem~\ref{thm:discrete-loss-poly-embeddable}: move from n-dimensional construction to n-1 dimensional construction (or add n-1 dim construction in appendix if it gets too hairy?)
%	\end{itemize}}

@@

% Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

@@

% OLD INTRO PARAGRAPH:
% Using tools from property elicitation, we show a tight relationship between such embeddings and the class of polyhedral (piecewise-linear convex) loss functions.
% In particular, by focusing on Bayes risks, we show that every discrete loss is embedded by some polyhedral loss, and every polyhedral loss function embeds some discrete loss.
% Moreover, we show that any polyhedral loss gives rise to a calibrated link function to the loss it embeds,
% thus giving a very general framework to construct consistent convex surrogates for arbitrary losses.

@@

To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.
We apply these tools to several polyhedral surrogates which have been proposed recently (\S~\ref{sec:applications}), showing in some cases that they are inconsistent for the desired target, but are consistent for a different target: the discrete loss they embed.

Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.\btw{Subtle distinction b/w polyhedral losses and losses with polyhedral Bayes risk.  I don't think we want that level of detail in the intro, and since we have an entire section on polyhedral embeddings, I think it's fine -J, 16 Sep 21}

@@

% \jessie{Take out this paragraph?}
%We go on to initiate a study of \emph{embedding dimension}: the minimal dimension for a given discrete loss to be so embedded.
%Our results give a complete characterization in the case of dimension 1; that is, real-valued surrogates.
%We find that a discrete loss can be embedded in the real line if and only if it is order-sensitive, meaning there is an ordering of the predictions such that the loss increases as one moves away from the correct prediction.
%We show further that order-sensitivity characterizes the existence of \emph{any} real-valued convex surrogate, implying that embeddings lose no generality.
%We conclude with preliminary results in higher dimensions and other future directions.

@@

Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
Define $\reals^\Y_+$ to be the nonnegative orthant in $\reals^\Y$, i.e., $\reals^\Y_+ = \{x \in \reals^\Y \mid \forall y\in\Y\; x_y \geq 0 \}$.
Let $\simplex = \{p\in\reals^{\Y}_+ \mid \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
% We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.
% While supervised algorithms learn hypothesis functions $h:\X \to \R$ that minimize expected loss over data representations and labels, one can abstract away the hypothesis function for simplicity and reason about generic reports.
% We first discuss this conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{subsec:calibration-links} how these notions relate to the usual $\X\times\Y$ setting considering features.
\raft{Tried to condense; old version commented out.}

A generic loss function, denoted $L:\R\to\reals^\Y_+$, maps a report (prediction) $r$ from a set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$.
When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.
\btw{RF: We got some feedback from Anish and others that the way we write generic losses was confusing.  I tried to rewrite this paragraph to emphasize that we use $L$ for generic losses, including surrogates, and $\ell$ for discrete losses, where we assume $\R$ is a finite set.  That way the idea that $\R$ is always finite is perhaps dispelled.}

We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where $\R$ is a finite set.
We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we assume $\R$ is a finite set.
%We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Surrogate losses will take $\R = \reals^d$ and be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.

%\jessie{In general, we shall denote discrete reports by $r \in \R$, and real-valued reports by $u \in \U$.}
For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.

Most of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
%
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex function of $u$ for each $y\in\Y$.
\end{definition}
%
For example, hinge loss is polyhedral, whereas logistic loss is not.

@@

To make headway, we will appeal to concepts and results from property elicitation.
This literature elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
In our case, this map will often be set-valued, meaning a single distribution could yield multiple optimal reports.
(For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.
%See the discussion following Definition~\ref{def:elicits} for notational conventions.% regarding $\R$, $\Gamma$, $\gamma$, $L$, $\ell$, etc.

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
Note that our definitions align such that discrete losses elicit finite properties (those with finite range). %; both are non-redundant in the correct senses.
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

% \begin{definition}[Consistency]\label{def:consistency}
%   A surrogate $L:\reals^d\to\reals^\Y_+$ and link $\psi:\reals^d\to\R$ is \emph{consistent} with a discrete loss $\ell:\R\to\reals^\Y_+$ if \raf{statement about distributions on $\X\times\Y$, limits of hypotheses, and Bayes opt hypotheses}
% \end{definition}

% \begin{definition}[Separated Link]\label{def:links}
%   Let discrete loss $\ell:\R\to\reals^\Y_+$ and surrogate $L:\reals^d\to\reals^\Y_+$ be given.
%   A \emph{link function} is a map $\psi:\reals^d\to\R$.
%   We say that a link $\psi$ is \emph{$\delta$-separated} for some $\delta > 0$ if for all $p \in \simplex$ and $u\in\reals^d$, we have
%   \begin{align*}
%     \inprod{p}{L(u)} - \inf_{u' \in \reals^d} \inprod{p}{L(u')} \geq \delta\left(\inprod{p}{\ell(\psi(u))} - \min_{r \in \R} \inprod{p}{\ell(r)}\right)~.
%   \end{align*}
%   A link is \emph{separated} if it is $\delta$-separated for some $\delta>0$.
% \end{definition}

\begin{definition}
  \label{def:calibrated}
  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Suppose we have the feature space $\X$ and label space $\Y$.
For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.
\bo{edited above slightly. I believe a technical definition of consistency would have a ``for all $\D$'', but we can probably skip that.}\jessie{Tried to make sure it had this technical correctness.}
\raf{Tried to clarify/correct the quantifiers.  OLD VERSION:
Let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
If $(L,\psi)$ is consistent, then for any sequence of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$ for all data distributions $D \in \Delta(\X \times \Y)$.}

@@

\bo{Should we comment on computing the $\epsilon$?}
\raf{Don't recall what we have to say... but this would be a great spot to do so.  Or at least make the point that the regret bounds (below) get better the higher $\epsilon$ is.}

>>>>

\usepackage{float}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{lmodern}
\usepackage{hyperref}       
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage[normalem]{ulem}
\usepackage{thm-restate}
\newcommand{\restatehack}[1]{}   
\usepackage{array}
\newcolumntype{R}{>{$}r<{$}} 
\newcolumntype{C}{>{$}c<{$}} 
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

\usepackage{mathtools, amsmath, amssymb, graphicx, verbatim, amsthm}
\usepackage{color}
\definecolor{darkblue}{rgb}{0.0,0.0,0.2}
\definecolor{darkgreen}{rgb}{0.0,0.3,0.0}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}
\usepackage{wrapfig}
\usepackage[font=small]{caption}
\usepackage{subcaption}
\usepackage[colorinlistoftodos,textsize=tiny]{todonotes} 
\usepackage{bbm}
\usepackage{xspace}

\usetikzlibrary{calc}
\newcommand{\Comments}{1}
\newcommand{\mynote}[2]{\ifnum\Comments=1\textcolor{#1}{#2}\fi}
\newcommand{\mytodo}[2]{\ifnum\Comments=1
  \todo[linecolor=#1!80!black,backgroundcolor=#1,bordercolor=#1!80!black]{#2}\fi}
\newcommand{\raf}[1]{\mynote{darkgreen}{[RF: #1]}}
\newcommand{\raft}[1]{\mytodo{green!20!white}{RF: #1}}
\newcommand{\jessie}[1]{\mynote{teal}{[JF: #1]}}
\newcommand{\jessiet}[1]{\mytodo{teal!20!white}{JF: #1}}
\newcommand{\proposedadd}[1]{\mynote{orange}{#1}}
\newcommand{\bo}[1]{\mynote{blue}{[Bo: #1]}}
\newcommand{\botodo}[1]{\mytodo{blue!20!white}{[Bo: #1]}}
\newcommand{\btw}[1]{\mytodo{gray!20!white}{BTW: #1}}
\ifnum\Comments=1               
  \setlength{\marginparwidth}{1in}
\fi

\newcommand{\reals}{\mathbb{R}}
\newcommand{\posreals}{\reals_{>0}}
\newcommand{\dom}{\mathrm{dom}}

@@

\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

\newcommand{\risk}[1]{\underline{#1}}
\newcommand{\inprod}[2]{\langle #1, #2 \rangle}
\newcommand{\relint}{\mathrm{relint}}
\newcommand{\inter}{\mathrm{inter}}
\newcommand{\expectedv}[3]{\E_{Y\sim{#3}} {#1}(#2,Y)}
\newcommand{\toto}{\rightrightarrows}
\newcommand{\strip}{\mathrm{strip}}
\newcommand{\trim}{\mathrm{trim}}
\newcommand{\red}{\mathrm{red}}
\newcommand{\trimred}{\mathrm{trim}}
\newcommand{\trimcover}{\mathrm{trim}}
\newcommand{\fplc}{finite-piecewise-linear and convex\xspace} 
\newcommand{\conv}{\mathrm{conv}}
\newcommand{\epi}{\mathrm{epi}}
\newcommand{\hyp}{\mathrm{hypo}}
\newcommand{\indopp}{\bar{\mathbbm{1}}}
\newcommand{\ones}{\mathbbm{1}}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}

@@

\title{An Embedding Framework for Consistent Polyhedral Surrogates}
\author{
 Jessie Finocchiaro \\
 \texttt{jefi8453@colorado.edu}
 \and
 Rafael Frongillo\\
 \texttt{raf@colorado.edu}
 \and
 Bo Waggoner\\
 \texttt{bwag@colorado.edu}
}
\date{
  University of Colorado Boulder
  \\[15pt]
  \today
}
\begin{document}

@@

\begin{abstract}
We formalize and study the natural approach of designing convex surrogate loss functions via embeddings, for problems such as classification, ranking, or structured prediction. 
In this approach, one embeds each of the finitely many predictions (e.g.\ rankings) as a point in $\reals^d$, assigns the original loss values to these points, and ``convexifies'' the loss in some way to obtain a surrogate.
We establish a strong connection between this approach and polyhedral (piecewise-linear convex) surrogate losses.
Given any polyhedral loss $L$, we give a construction of a link function through which $L$ is a consistent surrogate for the loss it embeds.
Conversely, we show how to construct a consistent polyhedral surrogate for any given discrete loss.
Our framework yields succinct proofs of consistency or inconsistency of various polyhedral surrogates in the literature, and for inconsistent surrogates, it further reveals the discrete losses for which these surrogates are consistent.
We show some additional structure of embeddings, such as the equivalence of embedding and matching Bayes risks, and the equivalence of various notions of non-redudancy.
Using these results, we establish that indirect elicitation, a necessary condition for consistency, is also sufficient when working with polyhedral surrogates.
\end{abstract}

@@

@@

A growing body of work seeks to design and analyze convex surrogates for particular target loss functions, and more broadly, understand the best empirical risk minimization bounds that can be found for a surrogate, for which consistency is a necessary condition.
For example, recent work has developed tools to bound the prediction dimension of the surrogate, meaning the dimension of the range of the surrogate hypothesis~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

@@

@@

To better understand existing polyhedral surrogates, we provide tools to find the discrete losses they embed (Proposition~\ref{prop:representative-embeds-restriction}).
In short, if one can identify a finite \emph{representative set} $\Sc$ of reports for a surrogate $L$, meaning $\Sc$ always contains an $L$-optimal report for any label distribution, then $L$ embeds $L|_\Sc$, the loss given by $L$ restricting to $\Sc$.

Underpinning our results are several observations which formalize the idea that polyhedral losses ``behave like'' discrete losses.
For example, discrete losses have polyhedral Bayes risks (as the minimum of finitely many linear functions), as do polyhedral losses (Lemma~\ref{lem:polyhedral-range-gamma}).
As a consequence, polyhedral losses always have finite representative sets, and restricting the loss to any such set is an embedding.

@@

@@

Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
Define $\reals^\Y_+$ to be the nonnegative orthant in $\reals^\Y$, i.e., $\reals^\Y_+ = \{x \in \reals^\Y \mid \forall y\in\Y\; x_y \geq 0 \}$.
Let $\simplex = \{p\in\reals^{\Y}_+ \mid \|p\|_1 = 1\}$ be the set of probability distributions on $\Y$, represented as vectors.
We will primarily focus on conditional distributions $p\in\simplex$ over labels, abstracting away the feature space $\X$; see \S~\ref{subsec:calibration-links} for a discussion of the joint distribution over $\X\times\Y$.

A generic loss function, denoted $L:\R\to\reals^\Y_+$, maps a report (prediction) $r$ from a set $\R$ to the vector of loss values $L(r) = (L(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{L(r)}$.
The \emph{Bayes risk} of a loss $L:\R\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{r\in\R} \inprod{p}{L(r)}$.
When restricting the domain of a loss $L$ from $\R$ to $\R'$, we write $L|_{\R'}$.

We assume that a given discrete prediction problem, such as classification, is given in the form of a discrete \emph{target loss} where $\R$ is a finite set.
We will denote target losses by $\ell:\R\to\reals^\Y_+$; when $\ell$ is written we assume $\R$ is a finite set.
Surrogate losses will take $\R = \reals^d$ and be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.

For example, 0-1 loss is a discrete loss with $\R = \Y = \{-1,1\}$
given by $\ellzo(r)_y = \Ind{r \neq y}$, with Bayes risk $\risk{\ellzo}(p) = 1-\max_{y\in\Y} p_y$.
Two important surrogates for $\ellzo$ are hinge loss $\hinge(u)_y = (1-yu)_+$, where $(x)_+ = \max(x,0)$, and logistic loss $L(u)_y = \log(1+\exp(-yu))$ for $u\in\reals$.
See Figure~\ref{fig:bayes-risks-01} for a visualization of the Bayes risks of 0-1, Hinge, and Logistic losses, respectively.

Most of the surrogate losses we consider will be \emph{polyhedral}, meaning piecewise linear and convex; we therefore briefly recall the relevant definitions.
In $\reals^d$, a \emph{polyhedral set} or \emph{polyhedron} is the intersection of a finite number of closed halfspaces.
A \emph{polytope} is a bounded polyhedral set.
A convex function $f:\reals^d\to\reals$ is \emph{polyhedral} if its epigraph is polyhedral, or equivalently, if it can be written as a pointwise maximum of a finite set of affine functions~\citep{rockafellar1997convex}.
\begin{definition}[Polyhedral loss]
  A loss $L: \reals^d \to \reals^{\Y}_+$ is \emph{polyhedral} if $L(u)_y$ is a polyhedral convex function of $u$ for each $y\in\Y$.
\end{definition}
For example, hinge loss is polyhedral, whereas logistic loss is not.

@@

To make headway, we will appeal to concepts and results from property elicitation.
This literature elevates the \emph{property}, or map from distributions to optimal reports, as a central object to study in its own right.
In our case, this map will often be set-valued, meaning a single distribution could yield multiple optimal reports.
(For example, when $p=(1/2,1/2)$, both $r=1$ and $r=-1$ optimize 0-1 loss.)
We will use double arrow notation to denote a (non-empty) set-valued map, so that $\Gamma: \simplex \toto \R$ is shorthand for $\Gamma: \simplex \to 2^{\R} \setminus \{\emptyset\}$.

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
By optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
Note that our definitions align such that discrete losses elicit finite properties (those with finite range). 
For example, the \emph{mode} is the 
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.

@@

\begin{definition}
  \label{def:calibrated}
  Let discrete loss $\ell:\R\to\reals^\Y_+$, proposed surrogate $L:\reals^d\to\reals^\Y_+$, and link function $\psi:\reals^d\to\R$ be given.
  We say $(L,\psi)$ is \emph{calibrated} with respect to $\ell$ if
for all $p \in \simplex$,
  \begin{equation}
    \label{eq:calibrated}
  \inf_{u \in \reals^d : \psi(u) \not\in \gamma(p)} \inprod{p}{L(u)} > \inf_{u \in \reals^d} \inprod{p}{L(u)}~.
  \end{equation}
  If $(L, \psi)$ is calibrated with respect to $\ell$, we call $\psi$ a \emph{calibrated link.}
\end{definition}
It is well-known in finite-outcome settings that calibration is equivalent to \emph{consistency}, in the following sense (cf.~\citep{bartlett2006convexity,zhang2004statistical,agarwal2015consistent}).
Suppose we have the feature space $\X$ and label space $\Y$.
For any data distribution $D \in \Delta(\X \times \Y)$, let $L^*$ be the best possible expected $L$-loss achieved by any hypothesis $H:\X\to\reals^d$, and $\ell^*$ the best expected $\ell$-loss for any hypothesis $h:\X\to\R$, respectively.
We say $(L,\psi)$ is consistent with respect to $\ell$ if, for all data distributions $D \in \Delta(\X \times \Y)$, and all sequences of surrogate hypotheses $H_1,H_2,\ldots$ whose $L$-loss limits to $L^*$, the $\ell$-loss of the sequence $\psi\circ H_1,\psi \circ H_2, \ldots$ limits to $\ell^*$.

@@
